---
title: "Conclusion"
format:
  html: 
    toc: false
    link-external-icon: false
    link-external-newwindow: false
---

```{r include = FALSE}
source(here::here("R", "buttons.R"))
```

In this module, you learned what R and RStudio are, how to install them, and how to find your way around the RStudio interface.

## R Readiness checklist

Before moving on, make sure you can genuinely do each of these, not just recognize them:

- [ ] Open RStudio and successfully run a line of code (e.g. `2 + 2`)
- [ ] Create a new R Script, write a line of code in it, and save it
- [ ] Point to each of the four panes and say what it's for
- [ ] Change at least one RStudio setting (e.g. theme, auto-save, or working directory)

## Hand-in assignment

This assignment can be used as part of a course. Through this assignment, you show that you have completed the checklist above. Prepare to hand in the following:

1.  A screenshot of RStudio showing an R Script open in the Source pane with at least one line of code, and the result of running that line visible in the Console pane.
2.  One sentence: if you had just loaded a dataset, which pane would you check to preview it, and why?
3.  A short note on which setting you changed, and why it's useful to you.

This isn't about getting a "correct" answer, it's proof that your setup works and that you can navigate it, which is everything you need for the next module.

You are now all set to continue with the next module. Here we take the first steps into writing R code. 

```{r}
#| echo: false
#| results: asis
next_module_button("https://www.openstatprog.com/first-steps/")
```
