---
title: "Software setup"
page-navigation: false
format:
  html: 
    toc: false
---

```{r, echo = FALSE, include = FALSE}
source(here::here("R", "buttons.R"))
```

Welcome to the *Software setup* module. In this module, you will:

1. [Learn what R is](/tutorials/whatis/index.qmd)
2. [Get step-by-step instructions for installing R and RStudio](/tutorials/install/index.qmd)
3. [Take a guided tour of the RStudio interface](/tutorials/guidedtour/index.qmd)

Each tutorial will comprise a series of interactive lessons with practice problems embedded throughout. Each tutorial section should be wrapped up with a knowledge quiz.

By the end, you'll be ready to start working in RStudio with confidence and begin your journey into data analysis using R.

## Learning Goals

After completing this module, you will be able to:

### Know what R and RStudio are:

1.  Learn what R is. 
2.  Learn what RStudio is. 
3.  Learn what open-source software is. 

### Install R and RStudio

1.  Learn how to install R.
2.  Learn how to install RStudio.
3.  Learn what to do if installing R and RStudio fails. 

### Get a guided tour

1.  Understand the R-studio layout 
2.  Learn how to change settings in RStudio.

Click the button below to get started with the first tutorial.

```{r}
#| echo: false
#| results: asis
begin_button("/tutorials/whatis/index.html")
```
